### 2015-09-09 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: edited hose stream report

\subsection{Instrumentation}
\label{sec:Instrumentation}
Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}. There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

% \subsection{Cold Flow Experimental Procedure}
% \label{sec:Cold_Flow_Procedure}

% \subsection{Water Flow Experimental Procedure}
% \label{sec:Water_Flow_Procedure}
A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure. All the experiments were conducted in either the East or West Structure; used a monitor %reference for specs? 2000 LPM (500 GPM)?
or 1~\nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns. Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.

@@

\subsubsection{Monitor Experiments}
\label{sec:Water_Flow_Monitor_Procedure}
A total of five sets of experiments were conducted using a monitor with a combination nozzle to flow water. Three of the tests (Tests 29, 30, and 33) occurred in the East Structure and two of the tests (Tests 16 and 17) occurred in the West Structure.

Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a monitor equipped with a combination nozzle. A schematic of the structure's layout during the two tests is presented in Fig.~\ref{fig:test_29-32_setup}. Each test began by flowing water with the nozzle aimed at the ceiling of Room C, as pictured in Fig.~\ref{fig:test_29_30_pic}. After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped. The monitor was adjusted so the nozzle was aimed at Door BC. Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. This entire procedure was repeated an additional time. A straight stream pattern was used during Test 29 and a narrow fog stream pattern was used during Test 30.

\begin{figure}[!ht]
\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
	\put(83,24){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
\end{overpic}
\caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
\label{fig:test_29-32_setup}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and at Door BC (bottom row) during Tests 29 and 30}
\label{fig:test_29_30_pic}
\end{figure}
\FloatBarrier

Test 33 varied from Tests 29 and 30 in multiple ways. During Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as shown in Fig.~\ref{fig:test_33_pic}. A schematic of the structure's layout during Test 33 is presented in Fig.~\ref{fig:test_33_34_setup}. The test began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

@@

%ADD TARGET DIMENSION%
Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle. The nozzle was aimed at two targets throughout the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall, and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated for the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

@@

\subsubsection{Handline Experiments}
\label{sec:Water_Flow_Handline_Procedure}
A total of five sets of experiments were conducted using a 1.75" handline with a combination nozzle to flow water. Three of the tests (Tests 31, 32, and 34) occurred in the East Structure and two of the tests (Tests 18 and 19) occurred in the West Structure.

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a combination nozzle attached to a 1.75" handline. The structure's layout during both tests was identical to the layout used in Tests 29 and 30 (Fig.~\ref{fig:test_29-32_setup}). Each test began by flowing water with the nozzle aimed at the ceiling of Room C in a fixed position, as pictured in Fig.~\ref{fig:test_31_32_pic}. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction for 30 seconds and then returned to the fixed position for 30 seconds. Next, the nozzle was rotated in the counterclockwise direction for 30 seconds and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, and the process was repeated with the handline aimed at Door BC. The entire procedure was then repeated an additional time. A straight stream pattern was used during Test 31 and a narrow fog stream pattern was used during Test 32.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}
\clearpage

Test 34 varied from Tests 31 and 32 in multiple ways. During Test 34, the handline was located inside Room C. The structure's layout during Test 34 was identical to the layout used in Test 33 (Fig.~\ref{fig:test_33_34_setup}). The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}. Next, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. This process were repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.

@@

%Where was the handline aimed?%
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated for narrow fog and wide fog streams.

@@

\section{Water Flow Test Results}
\label{sec:Water_Flow_Test_Results}

\subsection{Monitor Nozzle Experiments}

Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} and Fig.~\ref{fig:Test_16_BDP_A13_Avg_All} contain plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) and \nth{2} level, north side, west double doorway (A13), respectively, for Test 16. A similar set of plots was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A13_Avg_All}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[!ht]
%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
%\begin{tabular}{|l|c|c|c|c|}
%\cline{2-5}
%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
%\textit{Straight} & 
%%%%%Test 16%%%% 
%0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
%%%%%Test 17%%%% 
%0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 16%%%% 
%1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
%%%%%Test 17%%%% 
%0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 16%%%% 
%1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
%%%%%Test 17%%%% 
%0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
%\end{tabular}
%\label{table:Tests_16_17_BDP_A10_Avgs}
%\end{table}

%code for higher resolution in tabulated values
%\textit{Straight} & 0.84 & 0.94 & 0.73 & 0.69 \\ \hline
%\textit{Narrow Fog} & 1.41 & 1.00 & 0.75 & 0.75 \\ \hline
%\textit{Wide Fog} & 1.23 & 1.37 & 0.88 & 0.71 \\ \hline

%\begin{table}[!ht]
%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
%\begin{tabular}{|l|c|c|c|c|}
%\cline{2-5}
%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
%\textit{Straight} 	& 
%%%%%Test 16%%%% 
%2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%%Test 17%%%% 
%2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 16%%%% 
%4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%%Test 17%%%% 
%2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 16%%%% 
%3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%%Test 17%%%% 
%3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
%\end{tabular}
%\label{table:Tests_16_17_BDP_A13_Avgs}
%\end{table}

%code for higher resolution in tabulated values
%\textit{Straight} 	& 2.82 & 3.10 & 2.66 & 2.33 \\ \hline
%\textit{Narrow Fog} & 4.39 & 3.26 & 2.58 & 2.68 \\ \hline
%\textit{Wide Fog} 	& 3.92 & 4.37 & 3.14 & 2.76 \\ \hline

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%Test 17%%%% 
2.7 $\pm 0.4$ & 2.3 $\pm 0.8$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%Test 17%%%% 
2.6 $\pm 0.6$ & 2.7 $\pm 0.6$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%Test 17%%%% 
3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ 
\\ 
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A13_Avgs}
\end{table}

\subsection{Handline Experiments}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A13_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A13_Avg_All}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
%\cline{2-9}
%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\textit{Straight} 	& 
%%%%%Test 18%%%% 
%-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
%%%%%Test 19%%%% 
% 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 18%%%% 
% 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
%%%%%Test 19%%%% 
% 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 18%%%% 
% 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
%%%%%Test 19%%%% 
% 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
%\end{tabular}
%\label{table:Tests_18_19_BDP_A10_Avgs}
%\end{table}
%
%%code to increase resolution of tabulated values
%%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
%%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
%%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
%
%\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
%\cline{2-9}
%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\textit{Straight}  &
%%%%%Test 18%%%% 
%-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
%%%%%Test 19%%%%					
% 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 18%%%%
% 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
%%%%%Test 19%%%%
% 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 18%%%%
%3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
%%%%%Test 19%%%%
%3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
%\end{tabular}
%\label{table:Tests_18_19_BDP_A13_Avgs}
%\end{table}
%
%%code to increase resolution of tabulated values
%%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
%%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
%%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline

@@

\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 18}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\
\midrule 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Straight}  &
%%%%Test 18%%%% 
-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 18%%%%
 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$
 \\	\multicolumn{5}{c}{}	\\ 
\textit{Wide Fog} 	& 
%%%%Test 18%%%%
3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$
\\
\midrule
 & \multicolumn{4}{c}{\underline{Test 19}}	\\ 
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\
\midrule
\textit{Straight}  &
%%%%Test 19%%%%					
 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ 
 \\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 19%%%%
 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 19%%%%
3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$
\\
\bottomrule
\end{tabular}
\label{table:Tests_18_19_BDP_A13_Avgs}
\end{table}

@@

%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
%\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
%\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
%\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
%\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
%\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
%\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage

\chapter{Conclusions}
\label{chap:Conclusions}

\chapter{Future Work}
\label{chap:Future_Work}

>>>>

\subsection{Instrumentation}
\label{sec:Instrumentation}
There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. To avoid potential measurement errors due to external environmental conditions, only velocity data measured by BDPs located in interior doorways were considered during analyses. Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure. All the experiments were conducted in either the East or West Structure; used a monitor %reference for specs? 2000 LPM (500 GPM)?
or 1~\nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns. Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.

@@

\subsection{Monitor Experiments}
\label{sec:Water_Flow_Monitor_Procedure}
Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in the straight, narrow fog, and wide fog stream patterns. One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure.

Test 33 involved flowing water using a monitor equipped with a combination nozzle from Room C to the ceiling of Room B in the East Structure (Fig.~\ref{fig:test_33_pic}). A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

@@

% Add flow chart? %
Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle. The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated for the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

@@

\subsection{Handline Experiments}
\label{sec:Water_Flow_Handline_Procedure}
Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water. One test series, Test 34, occurred in the East Structure, and the two other series, Tests 18 and 19, occurred in the West Structure.

Test 34 involved flowing water using a 1.75" handline equipped with a combination nozzle located inside Room C. A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}. Next, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. This process were repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}

@@

% Where was the handline aimed? Add flow chart? %
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated for narrow fog and wide fog streams.

@@

\section{Monitor Nozzle Experiments}
\label{sec:monitor_results}

Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16. A similar figure was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.

@@

% \begin{figure}[!ht]
% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
% \caption{Average Velocity through Stairwell Door, Test 16, All Streams}
% \label{fig:Test_16_BDP_A10_Avg_All}
% \end{figure}

@@

@@

\section{Handline Experiments}
\label{sec:handline_results}

@@

% \begin{figure}[!ht]
% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
% \caption{Average Velocity through Stairwell Door, Test 18, All Streams}
% \label{fig:Test_18_BDP_A10_Avg_All}
% \end{figure}

% \clearpage

% \begin{figure}[!ht]
% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
% \caption{Average Velocity through Stairwell Door, Test 19, All Streams}
% \label{fig:Test_19_BDP_A10_Avg_All}
% \end{figure}

% \clearpage

@@

@@

@@

%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
%\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
%\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage

\chapter{Conclusions}
\label{chap:Conclusions}
\begin{enumerate}
\item Any movement of the hose stream increases the air flow through the structure
\item NF and WF move significantly more air than SS
\item No difference between rotating hose CW or CCW
\end{enumerate}

\chapter{Future Work}
\label{chap:Future_Work}
Need to determine if air movement caused by hose streams has significant impact on flow path and fire development in involved structure

compare to cold flow tests?
